---
title: "Assignment28"
author: "Emmadishetti Tejaswi(MA20M010)"
date: "04/12/2020"
output: html_document
---

```{r}
setwd("C:/Users/EMMADISHETTI TEJASWI/Desktop/applied stats/assignment/28")
df <- read.csv("Data.csv",header=TRUE)
dim(df)
str(df)
```
# 1)We will try to transform only price variable(dependent variable) and train multiple linear regression on training data and test it using mse
```{r}
summary(df$Price.in.Rupees)
df$Price.in.Rupees =log(df$Price.in.Rupees)
summary(df$Price.in.Rupees)
```
# Train-Test Split
```{r}
library(caTools)
set.seed(0)
split = sample.split(df,SplitRatio = 0.8)
training_set = subset(df,split == TRUE)
test_set = subset(df,split == FALSE)
```
# Training and Testing model
```{r}
lm_a = lm(Price.in.Rupees ~.,data=training_set)
train_a = predict(lm_a,training_set)
test_a = predict(lm_a,test_set)
mse=mean((test_set$Price.in.Rupees-test_a)^2)
mse
answer=(1-mse)
answer
```
# 2)Here we transform price variable again like before but instead,We will try to scale whole data and train Multiple linear Regression model again on newdataset and test it using mse
```{r}
df$Price.in.Rupees =exp(df$Price.in.Rupees)
summary(df$Price.in.Rupees)
df[,]=scale(df[,])
split = sample.split(df,SplitRatio = 0.8)
training_s = subset(df,split == TRUE)
test_s = subset(df,split == FALSE)
lm_a = lm(Price.in.Rupees ~.,data=training_s)
train_a= predict(lm_a,training_s)
test_a = predict(lm_a,test_s)
```
## Testing above Regression Model
```{r}
mse1=(mean((training_s$Price.in.Rupees-train_a)^2))
mse1
answer1=1-mse1
answer1
#it is performing good on unseen data also
mse2=mean((test_s$Price.in.Rupees-test_a)^2)
mse2 
answer2=1-mse2
answer2
```
# 3) Now we train SVM model on training set of new dataset using Linear Kernel and test it
```{r}
library('e1071')
svmfitR=svm(Price.in.Rupees ~.,data=training_s,kernel="linear",gamma=1,cost=0.01,scale=TRUE)
ypred=predict(svmfitR,test_s)
```
# Testing Svm model
```{r}
mse3=mean((ypred-test_s$Price.in.Rupees)^2)
mse3
answer3=1-mse3
answer3
```
# Hence by testing 3 cases using mean squared error,we can conclude that model is performing well on scaled data
